An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-04-14 EconGrowth.Rnw
Moved the partial residual plots to a reasonable place in the paper.

@@

>>>>

To qualitatively assess whether augmenting the Cobb-Douglas model with energy will be beneficial, we create partial residual plots as shown in Figures \ref{fig:CDPartialResidualsQ} - \ref{fig:CDPartialResidualsU} below. If a monotonic trend is observed on the graphs, we expect that energy augmentation will be beneficial. However, no strong monotonic tends are observed for any country, suggesting that energy augmentation of the Cobb-Douglas production function will not be beneficial.

@@

Similar to the analysis of the Cobb-Douglas model above, we make partial residual plots for the CES model in Figures \ref{fig:CESPartialResidualsQ} - \ref{fig:CESPartialResidualsU} below. Again, no strong monotonic trend is observed, suggesting the energy-augmentation of the CES model will not significantly improve the model.
